Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
anglais sur speed

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} technique are sometimes faster than the classical
algorithm. Our techniques are slower, but on the same order of magnitude as
the previous techniques.

>>>>

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm. The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.
